### 2019-10-01 defesa/tex/chapter/e3p.tex
wip

The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section. Even though its simple statement--it is short and uses only basic mathematics concepts--we were not able to find any work that dealt with this problem, or even related ones, either as its main goal or as a sub-problem. As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way. We try to give a review of some of those, and also make a case for the method we propose in terms of velocity of convergence and quality of the solutions.

We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$. A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$. In other words, the objective is to develop a method to find every solution of E3PNT.

@@

To prove that the number of solutions is limited by a constant, the problem is going to be modeled as finding the roots of an univariate polynomial of degree $12$.

@@

According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$. The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree, denoted by $\max_{i\in \{1, \dots, M\}}$, zero.

>>>>

The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section. Even though its simple statement--it is short and uses only basic mathematical concepts--we were not able to find any work on it, or even on related problems. 
As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way. We try to give a review of some of those, and also make a case for the method we propose in terms of velocity of convergence and quality of the solutions that it finds.

We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$. A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi]$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$. In other words, the goal is to develop a method to find every solution of E3PNT.

@@

The basis of the method developed on \autoref{chapter:ellipses_n} is that the number of solutions of E3PNT is limited and they can be found efficiently. At first we introduce a way to model

@@

According to \citeonline[p.~150]{powell}, any function of the form $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$ can be written as a real trigonometric polynomial of degree $j+k$ which can have up to $2(j+k)$ different roots in the interval $[0, 2\pi)$. The reason to bring up this fact is that $\xi(\theta)$ can be written as $\sum_i^M c_i \cos^{j_i}(\theta)\sin^{k_i}(\theta)$, for some $M \in \mathbb{N}$ and $c_1, \dots, c_m \in \R$, which implies that it can have up to $2$ times its degree, denoted by $\max_{i\in \{1, \dots, M\}} \{j_i, k_i\}$.
